### 2022-01-10 paper/issta22/experiment.tex
modify rq

\begin{enumerate}
  \item[\textbf{RQ1}:] How effective is our proposed evaluation model
    for generating diverse test cases? % self bleu score

  \item[\textbf{RQ2}:] How effective is our new test case generation
    using \cfg expansion?
  \item[\textbf{RQ3}:] How effective is our proposed evaluation model
    for finding failures given a linguistic capability?
\end{enumerate}

\subsection(Experiment Setup}

>>>>

\begin{enumerate}
\item[\textbf{RQ1}:] How effective is our proposed evaluation model
  for finding failures given a linguistic capability?
\item[\textbf{RQ2}:] How effective is our proposed model for
  generating diverse test cases? % self bleu score
\item[\textbf{RQ3}:]  How effective is our proposed model for
  detecting diverse type of errors? % retraining acc score
\item[\textbf{RQ4}:] How effective is our new test case generation
  using \cfg expansion? % ablation study

\end{enumerate}

\subsection{Experiment Setup}
